### 2024-08-10 mixed-models.qmd
20240810 - select best-fitting response distribution

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos"))); check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("parallel")
library("parallelly")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

Create an object with complete cases for generating the plots of individuals' -implied fantasy points by age and position:

@@

@@

>>>>

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos"))); check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("parallel")
library("parallelly")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

Create an object with complete cases for generating the plots of individuals' model-implied fantasy points by age and position:

@@

```{r}
fantasyPointsVector <- player_stats_seasonal_offense_subset$fantasy_points %>% 
    na.omit() %>% 
    as.vector()

player_stats_seasonal_offense_subset$fantasyPointsPosNoZeros <- player_stats_seasonal_offense_subset$fantasyPointsPos <- player_stats_seasonal_offense_subset$fantasy_points
player_stats_seasonal_offense_subset$fantasyPointsPos[player_stats_seasonal_offense_subset$fantasy_points < 0] <- 0
player_stats_seasonal_offense_subset$fantasyPointsPosNoZeros[player_stats_seasonal_offense_subset$fantasy_points <= 0] <- 0.01

fantasyPointsVectorPosNoZeros <- fantasyPointsVectorPos <- fantasyPointsVector
fantasyPointsVectorPos[fantasyPointsVector < 0] <- 0
fantasyPointsVectorPosNoZeros[fantasyPointsVector <= 0] <- 0.01
```

@@

```{r}
#| label: fig-cullenFreyGraphy
#| fig-cap: "Cullen and Frey Graph."

fitdistrplus::descdist(fantasyPointsVector)
```

```{r}
# all values
fit.norm <- fitdistrplus::fitdist(fantasyPointsVector, "norm")

# positive-only
fit.exp <- fitdist(fantasyPointsVectorPos, "exp")

# positive and no zeros
fit.gamma <- fitdistrplus::fitdist(fantasyPointsVectorPosNoZeros, "gamma")
fit.lognormal <- fitdistrplus::fitdist(fantasyPointsVectorPosNoZeros, "lnorm")
fit.weibull <- fitdistrplus::fitdist(fantasyPointsVectorPosNoZeros, "weibull")

# Model fit
AIC(fit.norm)
AIC(fit.exp)
AIC(fit.gamma) # fits best
AIC(fit.lognormal)
AIC(fit.weibull)
```

```{r}
plot(fit.norm)
```

```{r}
plot(fit.lognormal)
```

```{r}
plot(fit.gamma)
```

```{r}
plot(fit.exp)
```

```{r}
plot(fit.weibull)
```

```{r}
model_normal <- glm(
  formula = fantasy_points ~ 1,
  family = gaussian(),
  data = player_stats_seasonal_offense_subset,
  maxit = 100000)

model_gamma <- glm(
  formula = fantasyPointsPosNoZeros ~ 1,
  family = Gamma(),
  data = player_stats_seasonal_offense_subset,
  maxit = 100000)

sum(resid(model_normal)^2)
sum(resid(model_gamma)^2)

AIC(model_normal)
AIC(model_gamma)
```
